---
title: "Challenges in n-of-1 observational studies of acute event triggers: a simulation study of power, precision, and inferential classification with Cox regression"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

**n1coxeval** is a package of functions for use and evaluation of Cox regression
for n-of-1 observational studies of recurrent event triggers.

The script **main.R** uses this package to reproduce the analyses in the paper. 

The package may be installed from Github as follows:

```{r}

## Install the package
if(!require("remotes")){
    install.packages("remotes")
}
remotes::install_github("kholsteen/n1coxeval")
```

To reproduce the analyses, first update the following parameters in **main.R** to 
fit your computing environment:

```{r}
parent_output_dir <- "path/to/your/dir" ## Parent directory for simulation output
run_date <- "todaysdate" ## string subfolder name to create for storing this run of the analysis
num_parallel_workers <- 5 ## number of cores to use for parallel processing
```

Then run the script **main.R.** Expect the full analysis to take up to 12 hours
with 5 parallel workers. 

